Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-06 csf-2017/paper.tex
second high level motivation, secure compilation

% 3) Fully abstract compilation

>>>>

% 3) Fully abstract compilation
High-level languages provide guarantees such as encapsulation of local
state and well-bracketedness of function calls. These guarantees are
often relied upon when reasoning about the correctness and security of
a program. High-level programs are compiled to machine code, so in
order to rely on the correctness and security guarantees provided by
the high-level language, it needs to be proven that the translation
preserves these properties. Translated programs often interact with
machine code that is not translated from the same high-level language,
so in order to preserve the guarantees from the high-level languages,
the low-level machine needs to provide some kind of security
guarantees. In other words, a target of secure compilation needs to
provide some security guarantees. Modern processors provide many
security meassures, but very little in terms of guarantees. A machine
that provides some means of security guarantees is a capability machine.
